---
title: "Ford scholars alumni survey"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE,
                      fig.width = 8)

library(readxl)
library(tidyverse)
library(janitor)
library(googlesheets)
library(leaflet)
library(scales)
library(ggiraph)
library(bookdown)
library(skimr)

# gs_title("Alumni Engagement Survey Results") %>%
#      gs_download(to = "data/alumni_survey.xlsx",
#                  overwrite = T)

zips <- read_excel("data/TFFF Rural Zip Codes.xlsx") %>%
     clean_names() %>%
     select(-c(zip_code_map, tfff_1_1)) %>%
     remove_empty("rows") %>%
     mutate(zip_code_chr = as.character(zip_code))

data <- read_excel("data/alumni_survey.xlsx") %>%
     clean_names() %>%
     mutate(longitude = as.numeric(longitude)) %>%
     mutate(latitude = as.numeric(latitude)) %>%
     left_join(zips, by = c("what_is_the_zip_code_for_your_current_residence" = "zip_code_chr")) %>%
     mutate(age = 2018 - what_year_were_you_born) %>%
     mutate(lives_in_oregon = ifelse(is.na(tfff_classification), 
                   "Lives outside Oregon",
                   "Lives in Oregon")) %>%
     mutate(years_since_grad = 2018 - what_year_did_you_graduate_from_college) %>%
mutate(years_since_grad_grouped = case_when(
          years_since_grad < 2 ~ "0-2 years",
          years_since_grad < 5 & years_since_grad > 2 ~ "3-5 years",
          years_since_grad < 10 & years_since_grad < 5 ~ "6-10 years",
          years_since_grad < 15 & years_since_grad < 10 ~ "11-15 years",
          TRUE ~ "15+ years"
     )) %>%
       mutate(years_since_grad_grouped = factor(years_since_grad_grouped,
                                              levels = rev(c("0-2 years",
                                                         "3-5 years",
                                                         "6-10 years",
                                                         "11-15 years",
                                                         "15+ years")))) %>%
          mutate(highest_level_of_education_completed_or_in_progress = fct_rev(highest_level_of_education_completed_or_in_progress))

# Theme -------------------------------------------------------------------

tfff.dark.green <- "#265142"
tfff.light.green <- "#B5CC8E"
tfff.orange <- "#e65100"
tfff.yellow <- "#FBC02D"
tfff.blue <- "#283593"
tfff.red <- "#B71C1C"
tfff.brown <- "#51261C"
tfff.dark.gray <- "#545454"
tfff.medium.gray <- "#a8a8a8"
tfff.light.gray <- "#eeeeee"

# Functions

dk_pie_chart <- function(df) {
     df %>%
          ggplot(aes(x = "", 
                y = pct,
                fill = factor(item))) +
     geom_bar(stat = "identity",
              width = 1) +
     geom_text(aes(label = percent(pct)),
               position = position_stack(vjust = 0.5),
               color = "white") +
     coord_polar("y") +
     theme_void() +
     theme(legend.position = "bottom") +
          labs(fill = "") 
}

```


# Demographics

In total, there were 314 respondents.

## Where do respondents live?

### All respondents

Note: Respondents who listed the exact same zip codes are spread out slightly so they don't overlap. The dots do not show not exact locations of respondents.

```{r fig.height = 6}



data %>%
     mutate(longitude = jitter(longitude, factor = 2)) %>%
     mutate(latitude = jitter(latitude, factor = 2)) %>%
     leaflet() %>%
     addProviderTiles(providers$CartoDB.Positron) %>%
     addCircleMarkers(
          color = tfff.dark.green,
          fillOpacity = .5,
          popup = data$what_is_the_zip_code_for_your_current_residence
          )



```

### Within Oregon vs outside Oregon

72% of respondents live in Oregon. 28% live outside of Oregon.

```{r include = FALSE}

data %>%
     group_by(lives_in_oregon) %>%
     count() %>%
     ungroup() %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     ungroup()

```


### By Oregon county

This map shows the number of respondents per county (it only shows those who live in Oregon, obviously). Darker colors indicate higher numbers in a county. Hover over any county to see the exact number of respondents. 

```{r}


oregon_map <- map_data("county", "oregon")


oregon_map <- data %>%
     select(county) %>%
     group_by(county) %>%
     count() %>%
     ungroup() %>%
     mutate(county = str_to_lower(county)) %>%
     right_join(oregon_map, by = c("county" = "subregion")) %>%
     mutate(n = str_replace_na(n, "0")) %>%
     mutate(n = as.numeric(n))


m <- ggplot(oregon_map, 
            aes(x = long, 
                y = lat, 
                group = group,
                alpha = factor(n))) +
     geom_polygon_interactive(
          aes(tooltip = paste(str_to_title(county), 
                              " County\n",
                              n, 
                              " respondent(s)",
                              sep = "")),
          fill = tfff.dark.green,
          color = tfff.medium.gray) +
     coord_map() +
     theme_void() +
     theme(legend.position = "none")

ggiraph(code = print(m))

```

### Rural

In total, 36% of respondents live in zip codes TFFF considers rural. 64% live in urban zip codes. Note that this does not include those who live outside of Oregon.

```{r eval = F}

data %>%
     select(tfff_classification) %>%
     filter(!is.na(tfff_classification)) %>%
     group_by(tfff_classification) %>%
     count() %>%
     ungroup() %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     ungroup()

```


## Age

```{r}
data %>%
     ggplot(aes(x = age)) +
     # geom_histogram(fill = tfff.dark.green) +
     geom_bar(fill = tfff.dark.green) +
     labs(y = "Number of respondents",
          x = "Age") +
     theme_minimal() +
     scale_x_continuous(breaks = pretty_breaks(n = 10))

```

## Education

### Year respondents graduated from college

Note that some people were confused by whether to count their undergrad or higher levels. I only included answers that were clearly for undregrad.

```{r}
data %>%
     ggplot(aes(x = what_year_did_you_graduate_from_college)) +
     geom_bar(fill = tfff.dark.green) +
     labs(y = "Number of respondents",
          x = "Year graduated") +
     theme_minimal() +
     scale_x_continuous(breaks = pretty_breaks(n = 10))
```


### Years since graduation
The following graph shows the same data, but put into groups.
```{r}

data %>%
     group_by(years_since_grad_grouped) %>%
     count() %>%
     ungroup() %>%
     ggplot(aes(x = years_since_grad_grouped, 
                y = n)) +
     geom_col(fill = tfff.dark.green) +
     geom_text(aes(label = n),
               hjust = -.5,
               color = tfff.dark.green) +
     coord_flip() +
     theme_minimal() +
     scale_y_continuous(limits = c(0, 150)) +
     theme(axis.title = element_blank())
     

```


### Highest level of education

```{r}
data %>%
     group_by(highest_level_of_education_completed_or_in_progress) %>%
     count() %>%
     filter(highest_level_of_education_completed_or_in_progress != "Other (please specify)") %>%
     ungroup() %>%
     ggplot(aes(x = highest_level_of_education_completed_or_in_progress, 
                y = n)) +
     geom_col(fill = tfff.dark.green) +
     geom_text(aes(label = n),
               hjust = -.5,
               color = tfff.dark.green) +
     coord_flip() +
     theme_minimal() +
     scale_y_continuous(limits = c(0, 175)) +
     theme(axis.title = element_blank())
```




## Work

Principal industry (does not include those who said NA or listed other as their response).

```{r fig.height = 8}
data %>%
     select(which_of_the_following_best_describes_the_principal_industry_in_which_you_work) %>%
     group_by(which_of_the_following_best_describes_the_principal_industry_in_which_you_work) %>%
     count() %>%
     filter(which_of_the_following_best_describes_the_principal_industry_in_which_you_work != "NA") %>%
     ggplot(aes(x = reorder(which_of_the_following_best_describes_the_principal_industry_in_which_you_work, n),
                y = n)) +
     geom_col(fill = tfff.dark.green) +
     geom_text(aes(label = n),
               hjust = -.5,
               color = tfff.dark.green) +
     coord_flip() +
     theme_minimal() +
     scale_y_continuous(limits = c(0, 90)) +
     theme(axis.title = element_blank())
```

## Type of scholarship
```{r}
data %>%
     select(under_which_ford_family_program_did_you_receive_your_scholarship) %>%
     filter(!is.na(under_which_ford_family_program_did_you_receive_your_scholarship)) %>%
     group_by(under_which_ford_family_program_did_you_receive_your_scholarship) %>%
     count() %>%
     ungroup() %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     ungroup() %>%
     ggplot(aes(x = "", 
                y = pct,
                fill = factor(under_which_ford_family_program_did_you_receive_your_scholarship))) +
     geom_bar(stat = "identity",
              width = 1) +
     geom_text(aes(label = percent(pct)),
               position = position_stack(vjust = 0.5),
               color = "white") +
     coord_polar("y") +
     theme_void() +
     theme(legend.position = "bottom") +
     labs(fill = "") +
     scale_fill_manual(values = rev(c(tfff.dark.green, tfff.light.green, tfff.yellow)))
```













# Demographics across variables

## Within Oregon vs outside of Oregon

### By scholarship type

```{r}

data %>%
     select(city, county, tfff_classification, under_which_ford_family_program_did_you_receive_your_scholarship) %>%
     mutate(lives_in_oregon = str_replace_na(city, "Not in Oregon")) %>%
     mutate(lives_in_oregon = if_else(lives_in_oregon == "Not in Oregon", "Not in Oregon", "Oregon")) %>%
     group_by(lives_in_oregon, under_which_ford_family_program_did_you_receive_your_scholarship) %>%
     count() %>%
     group_by(under_which_ford_family_program_did_you_receive_your_scholarship) %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     ungroup() %>%
     mutate(lives_in_oregon = fct_rev(lives_in_oregon)) %>%
     ggplot(aes(x = "", 
                y = pct,
                fill = factor(lives_in_oregon))) +
     geom_bar(stat = "identity",
              width = 1) +
     geom_text(aes(label = percent(pct)),
               position = position_stack(vjust = 0.5),
               color = "white") +
     coord_polar("y") +
     theme_void() +
     theme(legend.position = "bottom") +
     labs(fill = "") +
     facet_wrap(~under_which_ford_family_program_did_you_receive_your_scholarship) +
     scale_fill_manual(values = c(tfff.dark.green, tfff.light.green))
     

```

## Rural

### Rural vs not rural by type of scholarship

```{r}

data %>%
     select(tfff_classification, under_which_ford_family_program_did_you_receive_your_scholarship) %>%
     filter(!is.na(tfff_classification)) %>%
     group_by(tfff_classification, under_which_ford_family_program_did_you_receive_your_scholarship) %>%
     count() %>%
     ungroup() %>%
     group_by(under_which_ford_family_program_did_you_receive_your_scholarship) %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     ungroup() %>%
     ggplot(aes(x = "", 
                y = pct,
                fill = factor(tfff_classification))) +
     geom_bar(stat = "identity",
              width = 1) +
     geom_text(aes(label = percent(pct)),
               position = position_stack(vjust = 0.5),
               color = "white") +
     coord_polar("y") +
     theme_void() +
     theme(legend.position = "bottom") +
     labs(fill = "") +
     facet_wrap(~under_which_ford_family_program_did_you_receive_your_scholarship) +
     scale_fill_manual(values = c(tfff.light.green, tfff.dark.green))
```




# Communications

## Awareness of Ford Scholar Alumni Association

### All respondents

```{r}


data %>%
     group_by(prior_to_receiving_the_email_for_this_survey_were_you_aware_of_the_existence_of_the_ford_scholar_alumni_association) %>%
     summarize(n = n()) %>%
     filter(!is.na(prior_to_receiving_the_email_for_this_survey_were_you_aware_of_the_existence_of_the_ford_scholar_alumni_association)) %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     set_names(c("item", "n", "pct")) %>%
     dk_pie_chart() +
     scale_fill_manual(values = rev(c(tfff.dark.green, tfff.light.green)))


```

### By whether they live in Oregon

```{r}
data %>%
     group_by(prior_to_receiving_the_email_for_this_survey_were_you_aware_of_the_existence_of_the_ford_scholar_alumni_association, lives_in_oregon) %>%
     summarize(n = n()) %>%
     filter(!is.na(prior_to_receiving_the_email_for_this_survey_were_you_aware_of_the_existence_of_the_ford_scholar_alumni_association)) %>%
     group_by(lives_in_oregon) %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     set_names(c("item", "lives_in_oregon", "n", "pct")) %>%
     dk_pie_chart() +
     scale_fill_manual(values = rev(c(tfff.dark.green, tfff.light.green))) +
     facet_wrap(~lives_in_oregon)


```


### By scholarship type

```{r}
data %>%
     group_by(prior_to_receiving_the_email_for_this_survey_were_you_aware_of_the_existence_of_the_ford_scholar_alumni_association, under_which_ford_family_program_did_you_receive_your_scholarship) %>%
     summarize(n = n()) %>%
     filter(!is.na(prior_to_receiving_the_email_for_this_survey_were_you_aware_of_the_existence_of_the_ford_scholar_alumni_association)) %>%
     group_by(under_which_ford_family_program_did_you_receive_your_scholarship) %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     set_names(c("item", "scholarship", "n", "pct")) %>%
     dk_pie_chart() +
     scale_fill_manual(values = rev(c(tfff.dark.green, tfff.light.green))) +
     facet_wrap(~scholarship)
```


## Communications they receive

### All respondents

```{r}
data %>%
     select(contains("which_communications")) %>%
     set_names(c("Quarterly e-newsletter",
                 "Annual alumni magazine",
                 "Emails",
                 "Social media posts",
                 "None")) %>%
     gather(key = "item", value = "response") %>%
     mutate(response = str_replace_na(response, "No")) %>%
     mutate(response = ifelse(response == "No", "No", "Yes")) %>%
     group_by(item) %>%
     count(response) %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     ungroup() %>%
     mutate(item = factor(item, levels = rev(c("Quarterly e-newsletter",
                 "Annual alumni magazine",
                 "Emails",
                 "Social media posts",
                 "None")))) %>%
     filter(response == "Yes") %>%
     ggplot(aes(x = item, y = pct)) +
     geom_col(fill = tfff.dark.green) +
          geom_text(aes(label = percent(pct)),
               hjust = -.35,
               color = tfff.dark.green) +
     coord_flip() +
     theme_minimal() +
     theme(axis.title = element_blank()) +
     scale_y_continuous(labels = percent,
                        limits = c(0, 1))
  
     
```

### By whether they live in Oregon

```{r}
data %>%
     select(contains("which_communications"), lives_in_oregon) %>%
     set_names(c("Quarterly e-newsletter",
                 "Annual alumni magazine",
                 "Emails",
                 "Social media posts",
                 "None",
                 "lives_in_oregon")) %>%
     gather(key = "item", value = "response", -lives_in_oregon) %>%
     mutate(response = str_replace_na(response, "No")) %>%
     mutate(response = ifelse(response == "No", "No", "Yes")) %>%
     group_by(item, lives_in_oregon) %>%
     count(response) %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     ungroup() %>%
     mutate(item = factor(item, levels = rev(c("Quarterly e-newsletter",
                 "Annual alumni magazine",
                 "Emails",
                 "Social media posts",
                 "None")))) %>%
     filter(response == "Yes") %>%
     ggplot(aes(x = item, y = pct)) +
     geom_col(fill = tfff.dark.green) +
          geom_text(aes(label = percent(pct)),
               hjust = -.35,
               color = tfff.dark.green) +
     coord_flip() +
     theme_minimal() +
     theme(axis.title = element_blank()) +
     scale_y_continuous(labels = percent,
                        limits = c(0, 1)) +
     facet_wrap(~lives_in_oregon)
  
```



# Engagement

# Familiarity with TFFF

```{r eval = FALSE, echo = FALSE, include = FALSE}

gitbook(split_by = "section+number", 
        number_sections = TRUE)

render_book("ford_scholar_alumni_survey.Rmd", 
            "bookdown::gitbook", 
            output_dir = "report")

```
