---
title: "Ford scholars alumni survey"
output:
  html_document:
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE,
                      fig.width = 8)

library(readxl)
library(tidyverse)
library(janitor)
library(googlesheets)
library(leaflet)
library(scales)
library(ggiraph)
library(bookdown)
library(skimr)
library(friendlyeval)
library(rlang)

source("data_functions_themes.R")


```


# Demographics

In total, there were 314 respondents.

## Type of scholarship
```{r fig.height = 3}

data %>%
     group_by(under_which_ford_family_program_did_you_receive_your_scholarship) %>%
     summarize(n = n()) %>%
     ggplot(aes(x = under_which_ford_family_program_did_you_receive_your_scholarship, y = n)) +
     geom_col(fill = tfff.dark.green) +
          geom_text(aes(label = n),
               vjust = -.5,
               color = tfff.dark.green) +
     dk_theme +
     theme(axis.title = element_blank()) +
     scale_y_continuous(limits = c(0, 225))

```

## Where do respondents live?

### All respondents

Note: Respondents who listed the exact same zip codes are spread out slightly so they don't overlap. The dots do not show not exact locations of respondents.

```{r fig.height = 6}



data %>%
     mutate(longitude = jitter(longitude, factor = 2)) %>%
     mutate(latitude = jitter(latitude, factor = 2)) %>%
     leaflet() %>%
     addProviderTiles(providers$CartoDB.Positron) %>%
     addCircleMarkers(
          color = tfff.dark.green,
          fillOpacity = .5,
          popup = data$what_is_the_zip_code_for_your_current_residence
          )



```

### Within Oregon vs outside Oregon


```{r fig.height = 2}

data %>%
     group_by(lives_in_oregon) %>%
     count() %>%
     ungroup() %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     ungroup() %>%
      ggplot(aes(x = lives_in_oregon, y = pct)) +
     geom_col(fill = tfff.dark.green) +
          geom_text(aes(label = percent(pct)),
               hjust = -.5,
               color = tfff.dark.green) +
     coord_flip() +
     dk_theme +
     theme(axis.title = element_blank()) +
     scale_y_continuous(limits = c(0, .9),
                        labels = percent)


```


### By Oregon county

This map shows the number of respondents per county (it only shows those who live in Oregon, obviously). Darker colors indicate higher numbers in a county. Hover over any county to see the exact number of respondents. 

```{r}


oregon_map <- map_data("county", "oregon")


oregon_map <- data %>%
     select(county) %>%
     group_by(county) %>%
     count() %>%
     ungroup() %>%
     mutate(county = str_to_lower(county)) %>%
     right_join(oregon_map, by = c("county" = "subregion")) %>%
     mutate(n = str_replace_na(n, "0")) %>%
     mutate(n = as.numeric(n))


m <- ggplot(oregon_map, 
            aes(x = long, 
                y = lat, 
                group = group,
                alpha = factor(n))) +
     geom_polygon_interactive(
          aes(tooltip = paste(str_to_title(county), 
                              " County\n",
                              n, 
                              " respondent(s)",
                              sep = "")),
          fill = tfff.dark.green,
          color = tfff.medium.gray) +
     coord_map() +
     theme_void() +
     theme(legend.position = "none")

ggiraph(code = print(m))

```

### Rural

```{r}

data %>%
     select(rural_or_not) %>%
     group_by(rural_or_not) %>%
     summarize(n = n()) %>%
     ggplot(aes(x = rural_or_not, y = n)) +
     geom_col(fill = tfff.dark.green) +
          geom_text(aes(label = n),
               vjust = -.5,
               color = tfff.dark.green) +
     dk_theme +
     theme(axis.title = element_blank()) +
     scale_y_continuous(limits = c(0, 175))
     

```


## Age

### Age of all respondents

```{r}
data %>%
     ggplot(aes(x = age)) +
     geom_bar(fill = tfff.dark.green) +
     dk_theme +
     labs(x = "Age",
          y = "Number of respondents") +
     scale_x_continuous(breaks = pretty_breaks(n = 10))

```

### Age of all respondents, grouped by decade

```{r}

data %>%
     filter(age_groups != "No info") %>%
     group_by(age_groups) %>%
     summarize(n = n()) %>%
     ggplot(aes(x = age_groups, y = n)) +
     geom_col(fill = tfff.dark.green) +
          geom_text(aes(label = n),
               vjust = -.5,
               color = tfff.dark.green) +
     dk_theme +
          labs(x = "Age",
          y = "Number of respondents") +
     scale_y_continuous(limits = c(0, 125))

```



## Education

### Year respondents graduated from college

Note that some people were confused by whether to count their undergrad or higher levels. I only included answers that were clearly for undregrad.

```{r}
data %>%
     ggplot(aes(x = what_year_did_you_graduate_from_college)) +
     geom_bar(fill = tfff.dark.green) +
     dk_theme +
     theme(axis.title  = element_blank()) +
     scale_x_continuous(breaks = pretty_breaks(n = 10))
```


### Years since graduation
The following graph shows the same data, but put into groups.
```{r}

data %>%
     group_by(years_since_grad_grouped) %>%
     count() %>%
     ungroup() %>%
     ggplot(aes(x = years_since_grad_grouped, 
                y = n)) +
     geom_col(fill = tfff.dark.green) +
     geom_text(aes(label = n),
               vjust = -.5,
               color = tfff.dark.green) +
     dk_theme +
     scale_y_continuous(limits = c(0, 150)) +
     theme(axis.title = element_blank())
     

```


### Highest level of education

```{r}
data %>%
     group_by(highest_level_of_education_completed_or_in_progress) %>%
     count() %>%
     filter(highest_level_of_education_completed_or_in_progress != "Other (please specify)") %>%
     ungroup() %>%
     ggplot(aes(x = highest_level_of_education_completed_or_in_progress, 
                y = n)) +
     geom_col(fill = tfff.dark.green) +
     geom_text(aes(label = n),
               vjust = -.5,
               color = tfff.dark.green) +
     dk_theme +
     scale_y_continuous(limits = c(0, 175)) +
     theme(axis.title = element_blank())
```




## Work

Principal industry (does not include those who said NA or listed other as their response).

```{r fig.height = 8}
data %>%
     select(which_of_the_following_best_describes_the_principal_industry_in_which_you_work) %>%
     group_by(which_of_the_following_best_describes_the_principal_industry_in_which_you_work) %>%
     count() %>%
     filter(which_of_the_following_best_describes_the_principal_industry_in_which_you_work != "NA") %>%
     ggplot(aes(x = reorder(which_of_the_following_best_describes_the_principal_industry_in_which_you_work, n),
                y = n)) +
     geom_col(fill = tfff.dark.green) +
     geom_text(aes(label = n),
               hjust = -.5,
               color = tfff.dark.green) +
     coord_flip() +
     dk_theme +
     scale_y_continuous(limits = c(0, 90)) +
     theme(axis.title = element_blank())
```
















# Communications

## Prior to receiving the email for this survey, were you aware of the existence of the Ford Scholar Alumni Association?


```{r fig.height = 2}
     

  data %>%
     group_by(prior_to_receiving_the_email_for_this_survey_were_you_aware_of_the_existence_of_the_ford_scholar_alumni_association) %>%
     summarize(n = n()) %>%
     filter(!is.na(prior_to_receiving_the_email_for_this_survey_were_you_aware_of_the_existence_of_the_ford_scholar_alumni_association)) %>%
     ggplot(aes(x = prior_to_receiving_the_email_for_this_survey_were_you_aware_of_the_existence_of_the_ford_scholar_alumni_association, y = n)) +
     geom_col(fill = tfff.dark.green) +
               geom_text(aes(label = n),
               hjust = -.5,
               color = tfff.dark.green) +
     coord_flip() +
     scale_fill_manual(values = c(tfff.light.green, tfff.dark.green)) +
     dk_theme +
     theme(axis.title = element_blank()) +
     scale_y_continuous(limits = c(0, 300))


     


```




## Which communications from the alumni association do you currently receive?

```{r fig.height = 3}
data %>%
     select(contains("which_communications")) %>%
     set_names(c("Quarterly e-newsletter",
                 "Annual alumni magazine",
                 "Emails",
                 "Social media posts",
                 "None")) %>%
     gather(key = "item", value = "response") %>%
     mutate(response = str_replace_na(response, "No")) %>%
     mutate(response = ifelse(response == "No", "No", "Yes")) %>%
     group_by(item) %>%
     count(response) %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     ungroup() %>%
     mutate(item = factor(item, levels = rev(c("Quarterly e-newsletter",
                                               "Annual alumni magazine",
                                               "Emails",
                                               "Social media posts",
                                               "None")))) %>%
     filter(response == "Yes") %>%
     ggplot(aes(x = item, y = pct)) +
     geom_col(fill = tfff.dark.green) +
     geom_text(aes(label = percent(pct)),
               hjust = -.35,
               color = tfff.dark.green) +
     coord_flip() +
     dk_theme +
     theme(axis.title = element_blank()) +
     scale_y_continuous(labels = percent,
                        limits = c(0, 1))


```


## How helpful are the following methods of the FSAA's communications?

```{r fig.height = 11}
data %>%
     select(contains("how_helpful")) %>%
     set_names(c("Quarterly e-newsletter",
                 "Annual alumni magazine",
                 "Emails",
                 "Social media posts")) %>%
     gather(key = "item", value = "response") %>%
     group_by(item, response) %>%
     summarize(n = n()) %>%
     filter(!is.na(response)) %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     mutate(response = factor(response, levels = c("Not at all helpful",
                                                   "Somewhat unhelpful",
                                                   "Neutral",
                                                   "Somewhat helpful",
                                                   "Very helpful"))) %>%
     filter(!is.na(response)) %>%
     ggplot(aes(x = response, y = pct)) +
     geom_col(fill = tfff.dark.green) +
          geom_text(aes(label = percent(pct)),
               vjust = -.35,
               color = tfff.dark.green) +
     dk_theme +
     theme(axis.title = element_blank(),
           legend.position = "none") +
     labs(fill = "") +
     facet_wrap(~item, ncol = 1,
                scale = "free_x") +
     scale_y_continuous(labels = percent,
                        limits = c(0, .6))
```


##  Rank the type of information you would like to see in alumni association communications, where 1 is the information you would most like to see and 6 is is the information you would least like to see.

```{r fig.height = 16}
data %>%
     select(contains("info_you_want_to_see")) %>%
     set_names(c("Event information",
                 "Community service opportunities",
                 "Ford Family Foundation notes",
                 "Alumni profiles",
                 "Information about current scholars",
                 "Professional development tips")) %>%
     gather(key = "item", value = "response") %>%
     group_by(item, response) %>%
     summarize(n = n()) %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     filter(!is.na(response)) %>%
     mutate(response = as.character(response)) %>%
     mutate(response = fct_inorder(response)) %>%
     ggplot(aes(x = response, 
                y = pct)) +
     geom_bar(stat = "identity", fill = tfff.dark.green) +
     geom_text(aes(label = percent(pct)),
               vjust = -.35,
               color = tfff.dark.green) +
     dk_theme +
     theme(legend.position = "none",
           axis.title = element_blank()) +
     facet_wrap(~item, ncol = 1,
                scale = "free_x") +
     scale_y_continuous(labels = percent,
                        limits = c(0, .5))
```


# Engagement



## How likely would you be to participate in the following types of opportunities if they were available? 

```{r fig.height=16}

data %>%
     select(contains("how_likely_would_you_be_to_participate_in_the_following_types_of_opportunities")) %>%
          set_names(c("Scholarship outreach at high schools or community colleges",
"Mentoring current scholars or alumni",
"Local community service projects",
"A regional alumni association event",
"Alumni association committee or board service",
"Professional leadership development training for alumni",
"Connect with alumni through private online portal for professional networking")) %>%
     gather(key = "item", value = "response") %>%
     group_by(item, response) %>%
     summarize(n = n()) %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     filter(!is.na(response)) %>%
     mutate(response = factor(response, levels = c("Very unlikely",
                                                   "Unlikely",
                                                   "Neutral",
                                                   "Likely",
                                                   "Very likely"))) %>%
     ggplot(aes(x = response, 
                y = pct)) +
     geom_bar(stat = "identity", fill = tfff.dark.green) +
     geom_text(aes(label = percent(pct)),
               vjust = -.35,
               color = tfff.dark.green) +
     dk_theme +
     theme(axis.title = element_blank()) +
     facet_wrap(~item, ncol = 1,
                scale = "free_x") +
     scale_y_continuous(labels = percent,
                        limits = c(0, .5))

```



## Rank from most important to least, from your perspective, the following reasons for engaging with the alumni association.

```{r fig.height = 13}
data %>%
     select(contains("reasons_for_engaging")) %>%
     select(-reasons_for_engaging_with_alumni_assocation_is_there_anything_not_listed_in_question_13_that_would_motivate_you_to_participate_in_alumni_activities) %>%
     set_names(c("Professional networking",
                 "Community service",
                 "Building community",
                 "Leadership development",
                 "Connection to and support of TFFF")) %>%
     gather(key = "item", value = "response") %>%
     group_by(item, response) %>%
     summarize(n = n()) %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     filter(!is.na(response)) %>%
     mutate(response = as.character(response)) %>%
     mutate(response = fct_inorder(response)) %>%
     ggplot(aes(x = response, 
                y = pct)) +
     geom_bar(stat = "identity", fill = tfff.dark.green) +
     geom_text(aes(label = percent(pct)),
               vjust = -.35,
               color = tfff.dark.green) +
     dk_theme +
     theme(legend.position = "none",
           axis.title = element_blank()) +
     facet_wrap(~item, ncol = 1,
                scale = "free_x") +
     scale_y_continuous(labels = percent,
                        limits = c(0, .5))
```


## Have you participated in past alumni association events?

```{r fig.height = 4}
data %>%
     select(contains("have_you_participated")) %>%
     set_names(c("1-2 events",
                 "3+ events",
                 "Board/committee service",
                 "Never attended")) %>%
     gather(key = "item", value = "response") %>%
     mutate(response = if_else(is.na(response), 
                               "No",
                               "Yes")) %>%
     group_by(item, response) %>%
     summarize(n = n()) %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
          filter(response == "Yes") %>%
     ggplot(aes(x = response, y = pct)) +
     geom_col(fill = tfff.dark.green) +
     geom_text(aes(label = percent(pct)),
               hjust = -.35,
               color = tfff.dark.green) +
     coord_flip() +
     theme_minimal() +
     theme(strip.text = element_text(size = 13, face = "bold"),
           panel.spacing = unit(1, "lines")) +
     theme(axis.title = element_blank(),
           axis.text.y = element_blank()) +
     facet_wrap(~item, ncol = 1) +
     scale_y_continuous(limits = c(0, 1),
                        labels = percent)
     


```

# The Ford Family Foundation

## How interested are you in engaging with the alumni association?

```{r}
data %>%
     select(how_interested_are_you_in_engaging_with_the_alumni_association) %>%
     gather(key = "item", value = "response") %>%
     group_by(item, response) %>%
     summarize(n = n()) %>%
     filter(!is.na(response)) %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     mutate(response = c("Somewhat not interested",
                                                   "Neutral",
                                                   "Somewhat interested",
                                                   "Very interested")) %>%
     mutate(response = factor(response, 
                              levels = c("Somewhat not interested",
                                                   "Neutral",
                                                   "Somewhat interested",
                                                   "Very interested"))) %>%
     ggplot(aes(x = response, y = pct)) +
     geom_col(fill = tfff.dark.green) +
          geom_text(aes(label = percent(pct)),
               vjust = -.35,
               color = tfff.dark.green) +
     dk_theme +
     theme(axis.title = element_blank(),
           legend.position = "none") +
     scale_y_continuous(labels = percent,
                        limits = c(0, .6))
```

## How interested are you in being engaged with The Ford Family Foundation?
```{r}
data %>%
     select(how_interested_are_you_in_being_engaged_with_the_ford_family_foundation) %>%
     gather(key = "item", value = "response") %>%
     group_by(item, response) %>%
     summarize(n = n()) %>%
     filter(!is.na(response)) %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     mutate(response = c("Somewhat not interested",
                                                   "Neutral",
                                                   "Somewhat interested",
                                                   "Very interested")) %>%
     mutate(response = factor(response, 
                              levels = c("Somewhat not interested",
                                                   "Neutral",
                                                   "Somewhat interested",
                                                   "Very interested"))) %>%
     ggplot(aes(x = response, y = pct)) +
     geom_col(fill = tfff.dark.green) +
          geom_text(aes(label = percent(pct)),
               vjust = -.35,
               color = tfff.dark.green) +
     dk_theme +
     theme(axis.title = element_blank(),
           legend.position = "none") +
     scale_y_continuous(labels = percent,
                        limits = c(0, .6))
```

## How aware are you about the work of the departments at The Ford Family Foundation?

```{r fig.height = 10}
data %>%
     select(contains("how_aware_are_you_about")) %>%
     set_names(c("FICB",
                 "Community Economic Development",
                 "Children, Youth, and Families",
                 "Postsecondary Success",
                 "Visual Arts")) %>%
     gather(key = "item", value = "response") %>%
     group_by(item, response) %>%
     summarize(n = n()) %>%
     filter(!is.na(response)) %>%
     mutate(pct = round(prop.table(n), digits = 2)) %>%
     mutate(response = factor(response, levels = c("No awareness",
                                                   "I've heard of it",
                                                   "Fairly aware",
                                                   "I know this work well"))) %>%
     filter(!is.na(response)) %>%
     ggplot(aes(x = response, y = pct)) +
     geom_col(fill = tfff.dark.green) +
          geom_text(aes(label = percent(pct)),
               vjust = -.35,
               color = tfff.dark.green) +
     dk_theme +
     theme(axis.title = element_blank(),
           legend.position = "none") +
     labs(fill = "") +
     facet_wrap(~item, ncol = 1,
                scale = "free_x") +
     scale_y_continuous(labels = percent,
                        limits = c(0, .6))
```

